\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-11 doc/sui14/iteration3.tex
refining texts for iteration3, more descriptions are needed

In our third iteration, we ask the question {\em can we build a system purely
using head orientation and visual feedback from the environment for target
selection?}

@@

In the learning stage, as the user scans over targets in their normal use, the
system attains the absolute orientation of each device from IR and motion
sensors. From this information it can abstract out their relative positions and
build an {\em adjacency map}. This process is transparent to the user, and the
map can be built without an explicit calibration phase.

This absolute orientation cannot be applied to all indoor environments, since
the user's movements through the space could change the relationships between
targets. However, with the constraint that the targets are spread around the
periphery, their relative orientations are stable (see
Figure~\ref{fig:third_principle}).

@@

After the map is created, the user can hold down on the touchpad to enter a
quasi-mode for refinement. In this quasi-mode, one device lights up at a time.
When the user turns their head in the direction of another device, the light
switches to that device. Therefore, the user can move between devices one at a
time with slight head movements. We implement this interaction by calculating
the user's direction of motion using a low-passed history of sensor
measurements and searching through the adjacency map for the nearest device in
that direction.

>>>>

In our third iteration, we ask the \changes{research} question --
{\em can we build a system purely using head orientation and visual
  feedback from the environment for target selection?}

@@

In the learning stage, as the user scans over targets in their normal
use, the system attains the absolute orientation of each device from
IR and motion sensors. From this information it can abstract out
\changes{the} relative positions \changes{of targets} and construct an
{\em adjacency map}. The absolute orientations in the map cannot be
applied to all indoor environments, since the user's movements through
the space could change the relationships between targets. However,
with the constraint that the targets are spread around the periphery
\changes{at similar distances}, their relative orientations are stable
(see Figure~\ref{fig:third_principle}). And since we are using IR at
the same time, the learning process is transparent to the user and the
map can be built without an explicit calibration phase.

@@

\changes{After the map is created, the user can enter a quasi-mode for
  refinement by holding down on the touchpad. In this quasi-mode, one
  device lights up at a time. When the user turns their head in the
  direction of another device, the light switches to that
  device. Therefore, the user can move between devices one at a time
  with slight head movements. This prediction is implemented by
  calculating the user's direction of motion using a low-passed
  history of sensor measurements and searching through the adjacency
  map for the nearest device in that direction.}
